How to be a good member of a scientific software community [Article v\versionnumber]

### 2021-06-11 templates/paper.tex
removed boilerplate, added a third checklist

Here you would explain what problem you are tackling and briefly motivate your work.

In this particular template, we have removed most of the usage examples which occur in \texttt{sample-document.tex} to provide a minimal template you can modify; however, we retain a couple of examples illustrating more unusual features of our templates/article class, such as the checklists, and information on algorithms and pseudocode.

Keep in mind, as you prepare your manuscript, that you should plan for a representative image  which will be used to highlight your article on the journal website and publications. Usually, this would be one of your figures, but it must also be uploaded separately upon article submission. We give specific guidelines for this image on the journal website in the section on article submission (see \url{https://livecomsjournal.github.io/authors/policies/index.html#article-submission}).

Additionally, for well-formatted manuscripts, we recommend that you let LaTeX handle figure/table placement for you as much as possible, so please avoid specifying strenuous float instructions like `[h!]` and `[H]` as much as possible.

\subsection{Scope}

Training articles are largely self-contained and introduce readers to the theory and/or typical procedures for a particular aspect of molecular simulation.

Training articles need not refer to specific software commands and procedures but may do so to further the pedagogical goals of the paper.

As needed, training articles are likely to display more details of calculations than typically are shown in research articles, for example, noting any mathematical principles or “tricks” used to derive key results.

The scope of the training article should be clearly defined.
This will often happen in a specific section or subsection in the article itself.

@@

>>>>

reveal the hidden curriculum -- what's expected of a software consumer, how to
ask for help, how to contribute

@@

\begin{checklist}{A good community}
\begin{itemize}
\item Helps users solve their problems
\item Is friendly and supportive when responding to questions
\item Encourages participation from users of all experience levels
\item Encourages respectful treatment of all community members, and calls out disrespectful behavior
\end{itemize}
\end{checklist}
